---
title: "Object type in R"
output: html_notebook
---

## What is R
R is an object-oriented programming language focused on analyzing and manipulating data. Everything in R is an object such as datasets, functions, plots, etc. R is one of the most popular language used by statisticians and data scientist. Thus, there're a lot of support communitites.

In this course, we'll use RStudio IDE for learning about R and financial analysis in R.

To download R, go to "https://cran.r-project.org/".
To download RStudio, go to "https://www.rstudio.com/products/rstudio/".

### Assigning Object in R: R objects can be assigned using the operator "<-" or "=". However, "<-" is preferred.
Object names can begin with letter. The name can contain letters, numbers, underscores, and periods.

### Object Type

Numeric
```{r}
#Integer
myint <- 5
typeof(myint)
print(myint)
```


```{r}
#Double
mydouble <- 2.3
print(mydouble)
```



Character
```{r}
mytext  <- "Hello World!" #Can use both " " and ' '
print(mytext)
```

Logical
```{r}
myanswer <- TRUE
myanswer
```


**Vector**

Construct vector manually. c() - concatenate()
```{r}
myvector  <- c(1,2,3,4,5)
print(myvector)
```

Sequence of consecutive integers.
```{r}
myvector2 <- 1:10
print(myvector2)
```

```{r}
#Create a vector of intergers from 10 to 20. Name it 'vector10.20'

vector10.20 <- 1:20
vector10.20  
```


Sequence - construc sequencing vector with function seq().
```{r}
myseq <- seq(from = 0, to = 20, by = 5)
print(myseq)
```

```{r}
#Create a sequencing vector of even number from 2 to 20. Use function seq( ). Name it 'even'.

even <- seq(from = 2, to = 20, by = 2)
print(even)
```


```{r}
myseq2 <- seq(0, 10, length.out = 21)
print(myseq2)
```

Repeated object
```{r}
myrep  <- rep(0, length.out = 6)
print(myrep)
```

```{r}
#Create a vector of number 1, repeating 10 times. Name it 'ones'.

ones <- rep(1, length.out = 10)
print(ones)
```



Indexing
```{r}
myvector3 <- c(1,3,5,7,9)
print(myvector3[3])
```


```{r}
print(myvector3[3:5])
```

```{r}
print(myvector3[c(-1,-2)])
```

```{r}
myvector3[c(1,4)]
```



Character Vector
```{r}
Name <- c("Captain America", "Iron Man", "Black Widow", "Thor", "Scarlet Witch")
print(Name)
print(Name[3])
```

Factor
```{r}
gender <- c("m", "m", "f", "m", "f")
gender <- factor(gender)
str(gender)
```


** Matrix vs data frame **
Matrix is similar to data frame but all the values are numeric.

Matrix
```{r}
matrixA <- matrix(1:15, nrow = 3, ncol = 5, byrow = TRUE)
matrixA
```

```{r}
matrixB <- matrix(1:15, nrow = 3, ncol = 5, byrow = FALSE)
matrixB
```




Construct data frame
```{r}
cast <- c("Chris Evans", "Robert Downey Jr.", "Scarlett Johansson", "Chris Hemsworth", "Elizabeth Olsen")
age  <- c(37, 53, 34, 35, 29)

Marvel.data <- data.frame(Name, gender, cast, age) #'Name' and 'gender' were created previously.
Marvel.data
```


List
```{r}
Marvel.list <- list(Name, gender, cast, TRUE, 1804)
Marvel.list
```

Calling element in list
```{r}
Marvel.list[[1]]
```
