---
title: "Exploratory Data Analysis"
output: html_notebook
---

##Exploratory data analysis (EDA) the very first step in a data project

*** Step 1: First approach to data ***

Quickly explore mtcars dataset

+ Variables in correct data types?

+ Missing values/ zeros/ NAs? 

+ Size of data

```{r}
#Loading
data(mtcars)
#structure of a dataset
str(mtcars)
```

```{r}
summary(mtcars)
```

```{r}
head(mtcars) #default shows first 6 rows
```


```{r}
tail(mtcars, 3)
```

```{r}
nrow(mtcars)
```

```{r}
ncol(mtcars)
```

```{r}
dim(mtcars)
```


*** Step 2: Explore categorical variables ***

+ Does all the categories make sense?

```{r}
table(mtcars$cyl)
```


*** Step 3: Explore numerical variables ***


Find the total value of each column
```{r}
colSums(mtcars)
```



Find an average of each column
```{r}
colMeans(mtcars)
```


Explore specific variable
```{r}
sum(mtcars$wt)
sum(mtcars[,6])

```

```{r}
mean(mtcars$mpg)
mean(mtcars[,1])
```


Correlation of variables
```{r}
cor(mtcars$hp, mtcars$mpg)
```


Names of each column/each row
```{r}
colnames(mtcars)
```

```{r}
rownames(mtcars)
```


*** Step 4: Quick visualization to explore the dataset***


```{r}
plot(x = mtcars$hp, y = mtcars$mpg, type = "p", col = "red")
```

```{r}
barplot(table(mtcars$cyl))
```



```{r}
plot(mtcars)
```



