---
title: "Data Visualization with base package"
output: html_notebook
---

*** Base Plot ***

Base plot is already in base package. No need to load library.
```{r}
speed    <- 20:60 #km/hr
time     <- 2 #hr
distance <- speed * time
distance

```

```{r}
#plot(x = speed, y = distance)      #plot() means scatter plot

#or 

plot(speed, distance)
```

*** Customizing plot ***

### Important base graphics parameters

+ main   - character string for chart title

+ xlab   - character string for x-axis label

+ ylab   - character string for y-axis label

+ col    - specify color

+ pch    - specify plotting symbol

+ lwd    - line width

+ lty    - line type

+ type   - type of plot (line, point, .)
  

```{r}
plot(x = speed, y = distance,       #specify what's on x-axis and y-axis
     main = "speed vs distance",    #chart title
     xlab = "speed (km/hr)",        #x-axis label
     ylab = "distance (km)",        #y-axis label
     col = "blue",                  #plot color
     pch = 18)                      #plot symbol
```


Different type arguments

+ "p"   - Points

+ "l"   - Lines

+ "b"   - Both points and lines

+ "c"   - The lines part alone of "b"

+ "o"   - Both points and lines "overplotted"

+ "h"   - Histogram like (or high-density) vertical lines

+ "n"   - No plotting


```{r}
par(mfrow = c(1,2)) #multiple plots in one screen
plot(speed, distance, type = "p", main = "Type 'p'")
plot(speed, distance, type = "l", main = "Type 'l'")
```

Multiple variables in one plot

```{r}
speed     <- 0:60
distance1 <- speed * time - 5
distance2 <- speed * time + 5
plot(speed, distance1, type = "l",col = "blue")
lines(speed, distance2, lty = 3, lwd = 3, col = "red")  #Try lty = 1 - 6

#Try
#points(speed, distance2, col = "red", pch = 8)
```




Multiple graphs in one plot
```{r}
x1 <- c(1, 3, 5, 7, 9)
x2 <- c(2, 4, 6, 8, 10)
y1 <- x1 + x2
y2 <- x2 - x1
y3 <- (x1 + x2)/2
```


```{r}
par(mfrow = c(2,3))             #Multiple graphs in one plot: Plots arranged in 2 rows 3 columns
plot(x1, y1, pch = 1, col = 1)  #Call plot() 6 times for 2 x 3 plots
plot(x1, y2, pch = 2, col = 2)
plot(x1, y3, pch = 3, col = 3)
plot(x2, y1, pch = 4, col = 4)
plot(x2, y2, pch = 5, col = 5)
plot(x2, y3, pch = 6, col = 6)
```


*** Visualization with 'diamonds' dataset ***
```{r}
#install.packages('ggplot2')  #If this is the first time you use ggplot, need to install first.
library(ggplot2)
data(diamonds)
head(diamonds)
```

Explore the dataset
```{r}
str(diamonds)    #check definition of each variable in slide deck
```


Scatter Plot
```{r}
plot(x = diamonds$carat, y = diamonds$price)
```

Customizing plot
```{r}
plot(x = diamonds$carat, y = diamonds$price, 
     main = "Diamond Price by Carat", 
     xlab = "Carat", 
     ylab = "Price", 
     col = "blue", 
     pch = 5)
```

