---
title: "Dealing with Date"
output: html_notebook
---


**Dealing with date**
```{r}
#Get today's date
today <- Sys.Date()
today
```

```{r}
class(today)
```

Convert character to date
```{r}
Character_date <- "2018-12-25"
class(Character_date)
```

```{r}
Christmas <- as.Date(Character_date)
Christmas
```

When printing, Character_date looks like Christmas. If we check, they are in different class.
```{r}
class(Christmas)
```

**Date Formats**
```{r}
#ISO 8601 Standard: YYYY-MM-DD
Dday <- as.Date("2018-12-25")
Dday
class(Dday)
```

```{r}
#Alternative Form: YYYY/MM/DD
Dday2 <- as.Date("2018/12/25")
Dday2
class(Dday2)
```

R cannot convert character string to date if it's not in the correct format.
```{r}
#Fail example
Dday3 <- as.Date("12/25/2018") #MM/DD/YYYY
Dday3
```

To fix this, we need to explicitly tell R the format we're using.
```{r}
Dday4 <- as.Date("12/25/2018", format = "%m/%d/%Y")
Dday4
class(Dday4)
```

**Date Formats**

+ %d - day of month (01-31)

+ %m - month (01 - 12)

+ %y - year 2 digits (00 - 99)

+ %Y - year 4 digits (0 - 9999)

+ %b - abbreviated month name (Jan, Feb, ...)

+ %B - full month name (April, May, ...)

**Day of week**
```{r}
weekdays(Sys.Date())
Sys.Date()
Sys.time()
```

```{r}
Songkran <- as.Date("2019-04-13")
weekdays(Songkran)
```

