---
title: "Importing and Managing Financial Data in R"
output: html_notebook
---

##Install relevant R packages
```{r}
install.packages('quantmod')
install.packages('Quandl')
install.packages('zoo')
install.packages('xts')
```

Load library
```{r}
library(quantmod)
library(Quandl)
library(zoo)
library(xts)
```

##Getting financial data with function getSymbols() from Yahoo Finance

Load PTTEP trading data from 2015 to 2018
```{r}
PTTEP <- getSymbols(Symbols = 'PTTEP.BK', src = 'yahoo', auto.assign = FALSE, warnings = FALSE, from = "2015-01-01", to = Sys.Date()) #Use to = Sys.Date() to download data until today
tail(PTTEP)
class(PTTEP)
```



Other data sources include

+ FRED: Federal Reserves Economic Data

+ OANDA: Foreign Exchange Data

+ Google Finance: No longer supporting

+ CSV File


You can also load financial data from CSV file
```{r}

#if cannot load data from yahoo, use csv file

#PTTEP <- read.zoo("data/PTTEP.csv", sep = ',', header = T)
#head(PTTEP)

```


**Explore financial data loaded**

OHLC: Open High Low Close

+ Open: Fist observed price

+ Close: Last observed price

+ High: Largest observed price

+ Low: Smallest observed price

+ Volume: Sum of contracts/shares traded

+ Adjusted Close: Closing price that has been adjusted to include corporate's action before the next day open e.g. stock splits, dividen, rights offerings 


**Function to extract a column or columns from loaded financial data**

+ Op() - open price

+ Hi() - High price

+ Lo() - Low price

+ Cl() - Close price

+ Vo() - Volume traded

+ Ad() - Adjusted close price

+ OHLC() - Open/High/Low/Close price

```{r}
pttep.open <- Op(PTTEP)
head(pttep.open)
```

```{r}
pttep.ad.close <- Ad(PTTEP)
head(pttep.ad.close, n = 10)
```

```{r}
pttep.ohlc <- OHLC(PTTEP)
head(pttep.ohlc)
```

```{r}
#Visualize time series data
plot(Ad(PTTEP))
```




